Child Poverty Interventions

### 2024-06-11 minos/outcomes/ChildPovReduction_Combined.Rmd
Additions and WIP plots for childPovReduction scripts

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

@@

@@

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'treated_relative') { tit <- 'Treated' }
  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

@@

## Treated Population

```{r}
SF12_change_simple(summary_group = 'treated_relative',
                   scen.list = scen.list.rel)
```

@@

## Treated Population

```{r}
SF12_change_simple(summary_group = 'treated_absolute',
                   scen.list = scen.list.abs)
```

### 2024-06-11 minos/outcomes/ChildPovReduction_plots.Rmd
Additions and WIP plots for childPovReduction scripts

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old6/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'treated') { tit <- 'Treated' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

@@

@@

```{r}
SF12_change_simple(summary_group = 'treated',
                   scen.list = scen.list.test)

SF12_change_percentage(summary_group = 'treated',
                       scen.list = scen.list.test)
```

@@

```{r}
#SF12_change_simple <- function(summary_group, scen.list) {

tit <- ' '
# if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
# if (summary_group == 'families') { tit <- 'Families' }

summary_group <- 'treated'
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')

@@

base.test <- filter(data, scen == 'baseline')
pov.test <- filter(data, scen == 'ChildPovertyReductionRELATIVE_2')

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old6/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'treated_relative') { tit <- 'Treated' }
  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

@@

  summary_group <- paste0(summary_group, '_income_quint2')

@@

```{r}
SF12_change_simple(summary_group = 'treated_relative',
                   scen.list = scen.list.test)

SF12_change_percentage(summary_group = 'treated_relative',
                       scen.list = scen.list.test)
```

@@

```{r}
SF12_change_simple <- function(summary_group, scen.list) {

  tit <- ' '
  if (summary_group == 'whole_pop') { tit <- 'Whole Population' }
  if (summary_group == 'families') { tit <- 'Families' }
  if (summary_group == 'treated_relative') { tit <- 'Treated' }
  if (summary_group == 'treated_absolute') { tit <- 'Treated' }
  if (summary_group == 'priority_any') { tit <- 'Any Priority Subgroup' }

  print(p1)
  print(p2)
  #print(p3)
}
```

## MENTAL HEALTH THRESHOLD

scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
summary_group <- 'men_illness_risk'

@@

plot_data <- data %>%
  group_by(scen, year, mental_health_risk) %>%
  summarise(count = mean(count)) %>%
  filter(mental_health_risk == 'TRUE')

ggplot(plot_data, aes(x = year, y = count, group = scen, color = scen)) +
  geom_point() +
  geom_line()

plot_data_2 <- data %>%
  filter(mental_health_risk == 'TRUE') %>%
  select(-prop, -mental_health_risk) %>%
  pivot_wider(names_from = scen,
              values_from = count) %>%
  mutate(MHR_diff = ChildPovertyReductionRELATIVE_2 - baseline) %>%
  select(run_id, year, MHR_diff) %>%
  group_by(year) %>%
  summarise(MHR_diff = mean(MHR_diff))

ggplot(data = plot_data_2, aes(x = year, y = MHR_diff)) +
  geom_point() +
  geom_line()

### 2024-06-11 minos/outcomes/child_poverty_reduction_vis.Rmd
Additions and WIP plots for childPovReduction scripts

```{r, include=FALSE}
#out.path <- here::here('output', 'default_config/')
out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
# int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)

>>>>

```{r, include=FALSE}
out.path <- here::here('output', 'default_config/')
#out.path <- here::here('output', 'scotland_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE,
                                    drop.zero.weight = TRUE)
# int1.rel <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
# int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionRELATIVE_2',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
int2.rel_fixed <- read_singular_local_out(out.path, 'ChildPovertyReductionSUSTAIN',
                                   drop.dead = TRUE,
                                   drop.zero.weight = TRUE)
# int3.abs <- read_singular_local_out(out.path, 'ChildPovertyReductionABSOLUTE',
#                                    drop.dead = TRUE,
#                                    drop.zero.weight = TRUE)
